Paper 2\thanks{Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}

### 2024-02-15 outputs/paper/paper.qmd
added new graph

# Model

>>>>

```{r}
# Parts of this code from R-charts
#https://r-charts.com/part-whole/stacked-bar-chart-ggplot2/
ggplot(cleaned_data, aes(x = follow_trump, fill = race)) +
  geom_bar(position = 'stack', color = 'black', stat = 'count') +
  labs(title = "Number of People Following Trump by Race",
       x = "Follows Trump",
       y = "Count") +
  scale_fill_manual(values = c('White / Caucasian' = 'lightblue', 'Black or African American' = 'lightcoral', 'Asian or Pacific Islander' = 'lightgreen', 'Hispanic' = 'plum',
                               'Other  (please specify)' = 'lightgoldenrodyellow')) +
  theme_minimal()

```
# Model

### 2024-02-15 outputs/paper/paper.tex
added new graph

@@

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Parts of this code from R{-}charts}
\CommentTok{\#https://r{-}charts.com/part{-}whole/stacked{-}bar{-}chart{-}ggplot2/}
\FunctionTok{ggplot}\NormalTok{(cleaned\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ follow\_trump, }\AttributeTok{fill =}\NormalTok{ race)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{\textquotesingle{}stack\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}black\textquotesingle{}}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}count\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Number of People Following Trump by Race"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Follows Trump"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}White / Caucasian\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightblue\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Black or African American\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightcoral\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Asian or Pacific Islander\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgreen\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}Hispanic\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}plum\textquotesingle{}}\NormalTok{,}
                               \StringTok{\textquotesingle{}Other  (please specify)\textquotesingle{}} \OtherTok{=} \StringTok{\textquotesingle{}lightgoldenrodyellow\textquotesingle{}}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}
